\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-04 gwnnDraft02.tex
plot and kappa

where $\gamma$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities.  $h^2 \Omega_{\gamma} $ is the energy density calculated using Eq.~(\ref{eqn::SNR}) with spectral index $\gamma$  and reference frequency $f_{\textrm{ref}}$. The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma \in (-8,-7,-6, ... , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$. Each curve will lay tangent to the PLI curve, more formally,

>>>>

where $\gamma$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities.  $h^2 \Omega_{\gamma} $ is the energy density calculated using Eq.~(\ref{eqn::SNR}) with spectral index $\gamma$  and reference frequency $f_{\textrm{ref}}$. The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\gamma$ and for some fixed threshold value of $\rho_{th}$. Each curve will lay tangent to the PLI curve, more formally,
